Nested Stochastic Block Models Applied to the Analysis of Single Cell Data

### 2021-04-16 manuscript.tex
udpate runtimes for paul15
New figure for label transfer

\begin{figure}[H]
\centering
\includegraphics[keepaspectratio,width=\textwidth,height=0.55\textheight]{Figure_Hemato_Lineage.png}
\caption[]{Analysis of hematopoietic differentiation. Each panel presents a low dimensional embedding of single cells next to a radial tree representation of the nSBM hierarchy. Cells are colored according to groupings at level 2 of the hierarchy, group 0 marks the most primitive population (A). In subsequent panels, cells are colored using a signature of erythroid lineage (B), monocytes (C) or neutrophils (D).}\label{Figure_Hemato_Lineage}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[keepaspectratio,width=\textwidth,height=0.55\textheight]{Figure_Label_Transfer.png}
\caption[]{Label transfer using SBM. Annotated data from Chromium 10X (A) and  MARS-seq (B) were merged using Harmony. MARS-seq cells were relabeled according to the \emph{k}NN graph (C) or by exploiting the Stochastic Block Model (D). }\label{Figure_Label_Transfer}
\end{figure}

@@

\begin{table}[h!]
\centering
 \begin{tabular}{|| l c c c c c ||}
%  \begin{tabular}{|| m{7em} | m{5em} | m{7em} | m{7em} | m{5em} ||}
 \hline
 \textbf{Dataset} & \textbf{Cells} & \textbf{Edges} & \textbf{Leiden} & \textbf{PPBM} & \textbf{NSBM} \\ [0.5ex] 
 \hline\hline
% sc-mixology \cite{tian_2019} & 860 & 01:11 & 00:03 & 0.884 \\ 
 %\hline
 Chromium 10x \cite{mereu_2020} & 1523 & 21447 & 00:24 & 01:34 & 03:29\\ 
 \hline
 Quartz-seq2 \cite{mereu_2020} & 1266 & 14603 & 00:16 & 00:30 & 02:10 \\
 \hline
 MARS-seq \cite{mereu_2020} & 1401 & 21756 & 00:24 & 01:10 & 06:11 \\
 \hline
 iCELL8 \cite{mereu_2020} & 1830 & 30636 & 00:34 & 01:31 & 09:06 \\
 \hline
 Paul15 \cite{paul_2015} & 2730 & 51475 & 01:21 & 03:35 & 12:17\\ 
 \hline
 Planaria \cite{plass_2018} & 21612 & 173667 & 06:32 & 34:12 & 3:17:08 \\
 \hline
% 4 & 545 & 18744 & 7560 \\
% \hline
% 5 & 88 & 788 & 6344 \\ [1ex] 
% \hline
\end{tabular}
\caption{Time required to minimise the nSBM using the default minimization method compared to the greedy merge-split MCMC. Times are expressed in mm:ss. Partition overlap measures concordance between the two models over the full hierarchy. Timing is the average after 3 initialisations.}
\label{Table1}
\end{table}

>>>>

\begin{figure}[H]
\centering
\includegraphics[keepaspectratio,width=\textwidth,width=0.55\textheight]{Figure_Hemato_Lineage.png}
\caption[]{Analysis of hematopoietic differentiation. Each panel presents a low dimensional embedding of single cells next to a radial tree representation of the nSBM hierarchy. Cells are colored according to groupings at level 2 of the hierarchy, group 0 marks the most primitive population (A). In subsequent panels, cells are colored using a signature of erythroid lineage (B), monocytes (C) or neutrophils (D).}\label{Figure_Hemato_Lineage}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[keepaspectratio,width=\textwidth,width=0.55\textheight]{Figure_Label_Transfer.png}
\caption[]{Label transfer using SBM. Annotated data from Chromium 10X (A) and  MARS-seq (B) were merged using Harmony. MARS-seq cells were relabeled according to the \emph{k}NN graph (C) or by exploiting the Stochastic Block Model (D). }\label{Figure_Label_Transfer}
\end{figure}

@@

\begin{table}[h!]
\centering
 \begin{tabular}{|| l c c c c c ||}
%  \begin{tabular}{|| m{7em} | m{5em} | m{7em} | m{7em} | m{5em} ||}
 \hline
 \textbf{Dataset} & \textbf{Cells} & \textbf{Edges} & \textbf{Leiden} & \textbf{PPBM} & \textbf{NSBM} \\ [0.5ex] 
 \hline\hline
% sc-mixology \cite{tian_2019} & 860 & 01:11 & 00:03 & 0.884 \\ 
 %\hline
 Chromium 10x \cite{mereu_2020} & 1523 & 21447 & 00:24 & 01:34 & 03:29\\ 
 \hline
 Quartz-seq2 \cite{mereu_2020} & 1266 & 14603 & 00:16 & 00:30 & 02:10 \\
 \hline
 MARS-seq \cite{mereu_2020} & 1401 & 21756 & 00:24 & 01:10 & 06:11 \\
 \hline
 iCELL8 \cite{mereu_2020} & 1830 & 30636 & 00:34 & 01:31 & 09:06 \\
 \hline
 Paul15 \cite{paul_2015} & 2730 & 15444 & 00:34 & 02:53 & 06:55\\ 
 \hline
 Planaria \cite{plass_2018} & 21612 & 173667 & 06:32 & 34:12 & 3:17:08 \\
 \hline
% 4 & 545 & 18744 & 7560 \\
% \hline
% 5 & 88 & 788 & 6344 \\ [1ex] 
% \hline
\end{tabular}
\caption{Time required to minimise the nSBM using the default minimization method compared to the greedy merge-split MCMC. Times are expressed in mm:ss. Partition overlap measures concordance between the two models over the full hierarchy. Timing is the average after 3 initialisations.}
\label{Table1}
\end{table}
